More on Slavnov Products of Spin Chains and KP Hierarchy Tau Functions

### 2025-05-27 draft.tex
remove today in date field -- new arxiv rules
arxiv v1

\bibliography{/home/thiago/Sync/wiki/database/bib-database.bib}

@@

\begin{abstract}
 Connections between classical and quantum integrable systems are
 analyzed from the viewpoint of Slavnov products of Bethe states. It
 is well known that, modulo model dependent aspects, the functional
 structure of Slavnov products generally takes the form of
 determinants. Building on recent results on the structure of rational
 and trigonometric models, we show that, provided certain conditions
 are satisfied, the Slavnov product of a given model can be
 interpreted as a tau function of the KP hierarchy, thus extending
 known results in a more general setting. Moreover, we show that
 Slavnov products can be expanded in terms of other tau functions. We
 also prove that their homogeneous limit can be systematically
 expressed as a Wronskian of functions related to the eigenvalues of
 the transfer matrices.  Finally, we compute the Baker–Akhiezer
 functions associated with these Slavnov products and show that, apart
 from a universal multiplicative factor, they admit a closed
 determinantal representation.
\end{abstract}

\date{\today}
\keywords{Integrability, field theories, lattice models, correlation functions, bethe ansatz}
\subjclass[2020]{81T40, 81U15, 82B20, 82B21, 82B23}
%81T40 : Two-dimensional field theories, conformal field theories, etc. in quantum mechanics
%81U15 : Exactly and quasi-solvable systems arising in quantum theory
%82B20 : Lattice systems (Ising, dimer, Potts, etc.) and systems on graphs arising in equilibrium statistical mechanics
%82B21 : Continuum models (systems of particles, etc.) arising in equilibrium statistical mechanics
%82B23 : Exactly solvable models; Bethe ansatz

@@

%\subsubsection*{Acknowledgments}
%I would like to thank the Fluminense Federal University for

\printbibliography

>>>>

@@

\begin{abstract}
 Connections between classical and quantum integrable systems are analyzed from the viewpoint of Slavnov products of Bethe states. It is well known that, modulo model dependent aspects, the functional structure of Slavnov products generally takes the form of determinants. Building on recent results on the structure of rational and trigonometric models, we show that, provided certain conditions are satisfied, the Slavnov product of a given model can be interpreted as a tau function of the KP hierarchy, thus extending known results in a more general setting. Moreover, we show that Slavnov products can be expanded in terms of other tau functions. We also prove that their homogeneous limit can be systematically expressed as a Wronskian of functions related to the eigenvalues of the transfer matrices.  Finally, we compute the Baker-Akhiezer functions associated with these Slavnov products and show that, apart from a universal multiplicative factor, they admit a closed determinantal representation.
\end{abstract}

\keywords{Integrability, field theories, lattice models, correlation functions, bethe ansatz}
\subjclass[2020]{81T40, 81U15, 82B20, 82B21, 82B23}
%81T40 : Two-dimensional field theories, conformal field theories, etc. in quantum mechanics
%81U15 : Exactly and quasi-solvable systems arising in quantum theory
%82B20 : Lattice systems (Ising, dimer, Potts, etc.) and systems on graphs arising in equilibrium statistical mechanics
%82B21 : Continuum models (systems of particles, etc.) arising in equilibrium statistical mechanics
%82B23 : Exactly solvable models; Bethe ansatz

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Acknowledgments}

I would like to express my sincere gratitude to the Department of
Physics at Fluminense Federal University for providing an excellent
research environment and for their support of this work.

\bibliographystyle{utphys}
\bibliography{bib-database.bib}
